Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-07-24 tex/test-WW-type-00z.tex
alexei

Experimental collaborations often define asymmetries in terms of counts 
$N(\phi_h)$. This means the kinematic prefactors $p_i$ %and $1/(x\,y\,Q^2)$ 
are included in the numerators or denominators of the asymmetries which
are averaged over $y$ within experimental kinematics. We will call the 
corresponding asymmetries $\asympre{XY}{\rm weight}$.
For instance, in the unpolarized case one has 
\be
	N(x,\dots,\phi) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
		+ \cos\phi\;\asympre{UU}{\cos\phi_h}(x,\dots)
		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
\ee
where $N_0$ denotes the total ($\phi_h$--averaged) number of counts 
and the dots indicate further kinematic variables in the kinematic 
bin of interest (which may also be averaged over).
It would be preferable if asymmetries were analyzed with known kinematic 
prefactors divided out on event-by-event basis. One could then directly 
compare asymmetries $\asym{XY}{\rm weight}$ measured in different 
experiments and kinematics, and focus on effects of evolution 
or power suppression for twist-3. In practice, often the kinematic 
factors were included. We will define and comment on the explicit 
expressions as needed.

@@

The leading--twist 6 TMDs 
$f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
in the sense that in WW-type approximation all other TMDs and FFs 
can either be expressed in terms of these basis functions or vanish.
Below we shall see that, under the assumption of the validity of WW-type 
approximations, it is possible to express all SIDIS structure functions
in terms of the basis functions. 
Notice that SIDIS alone is of course not sufficient to determine the basis
functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
It is crucial to take advantage of  Drell--Yan process for TMDs
and other processes 
play also important roles.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}
\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.8\textwidth]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf} 
\vspace{-5mm}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
\includegraphics[width=0.9\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
\caption{\label{aulsinphi_jlab} 
	$A_{UL}^{\sin\phi_h}$ for proton target vs $x$ from WW-type 
	approximation in comparison to data for the following hadrons.
	Upper panel left: $\pi^\pm$ from HERMES \cite{Airapetian:2005jc}.
	Upper panel right: $\pi^0$ from HERMES (blue) \cite{Airapetian:2001eg} 
	and JLab (red) \cite{Jawalkar:2017ube}.
	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2018ovx}.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pip.pdf}
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pim.pdf}
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
\caption{\label{autsinphis} 
 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which 
	is predicted to vanish in the WW-type approximation, in 
	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} and HERMES data \cite{Schnell:2010zza}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
\caption{\label{autsin2phihphis} 
	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison to preliminary COMPASS data~\cite{Parsamyan:2013fia}, and 	
	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to  
	preliminary HERMES data~\cite{Schnell:2010zza}.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Experimental collaborations often define asymmetries in terms of counts 
$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$ 
are included in the numerators or denominators of the asymmetries which
are averaged over $y$ within experimental kinematics. We will call the 
corresponding asymmetries $\asympre{XY}{\rm weight}$.
For instance, in the unpolarized case one has 
\be
	N(x,\dots,\phi) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
		+ \cos\phi\;\asympre{UU}{\cos\phi_h}(x,\dots)
		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
\ee
where $N_0$ denotes the total ($\phi_h$--averaged) number of counts 
and the dots indicate further kinematic variables in the kinematic 
bin of interest (which may also be averaged over).
It would be preferable if asymmetries were analyzed with known kinematic 
prefactors divided out on event-by-event basis. One could then directly 
compare asymmetries $\asym{XY}{\rm weight}$ measured in different 
experiments and kinematics, and focus on effects of evolution 
or power suppression for twist-3. In practice, often the kinematic 
factors were included. We will define and comment on the explicit 
expressions as needed.

@@

The leading--twist 6 TMDs 
$f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
in the sense that in WW-type approximation all other TMDs and FFs 
can either be expressed in terms of these basis functions or vanish.
Below we shall see that, under the assumption of the validity of WW-type 
approximations, it is possible to express all SIDIS structure functions
in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine the basis
functions uniquely: the 8 basis functions appear in 6 SIDIS structure functions.
It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
play also important roles.}
%Notice that SIDIS alone is of course not sufficient to determine the basis
%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
%It is crucial to take advantage of  Drell--Yan process for TMDs
%and other processes 
%play also important roles.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}
\includegraphics[width=0.55\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.9\textwidth]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
\includegraphics[width=0.55\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf} 
\vspace{-5mm}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
\includegraphics[width=0.8\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
\caption{\label{aulsinphi_jlab} 
	$A_{UL}^{\sin\phi_h}$ for proton target vs $x$ from WW-type 
	approximation in comparison to data for the following hadrons.
	Upper panel left: $\pi^\pm$ from HERMES \cite{Airapetian:2005jc}.
	Upper panel right: $\pi^0$ from HERMES (blue) \cite{Airapetian:2001eg} 
	and JLab (red) \cite{Jawalkar:2017ube}.
	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2018ovx}.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pip.pdf}
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pim.pdf}
\includegraphics[width=0.55\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
\caption{\label{autsinphis} 
 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which 
	is predicted to vanish in the WW-type approximation, in 
	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} and HERMES data \cite{Schnell:2010zza}.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
\includegraphics[width=0.55\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
\caption{\label{autsin2phihphis} 
	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison to preliminary COMPASS data~\cite{Parsamyan:2013fia}, and 	
	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to  
	preliminary HERMES data~\cite{Schnell:2010zza}.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
